A classifying space for a group \(G\) is a space \(X\) such that the fundamental group of \(X\) is \(G\) and all higher homotopy groups of $X$ are trivial.
In this paper we will be concerned with the $K(\pi,1)$ conjecture for Artin groups, which states that the configuration space $Y_W$ for any Coxeter group $W$ is a classifying space for the Artin group $G_W$.  This conjecture emerges as a generalisation of the result for Coxeter groups of type $A_n$ and is originally attributed to Arnol'd, Brieskorn, Pham and Thom in \cite{paris_kpi1_2014}. See also \cite{charney_davis_pi_1995} for a good overview of the history of the conjecture.

We will focus on the work of Paolini and Salvetti, \emph{Proof of the \(K(\pi, 1)\) conjecture for affine Artin groups} \cite{paolini_salvetti_kpi1_2021}. We will review some theorems therein and provide relevant background. The theorem which is the namesake of \cite{paolini_salvetti_kpi1_2021} relies on proving a chain of homotopy equivalences \eqref{eqn:proof_overview}. Detailing two of these homotopy equivalences is the aim of this work. A strong theme will be the involvement of posets and related structures, hence this work's title. We will begin by providing a birds eye view of the conjecture and the  main results of \cite{paolini_salvetti_kpi1_2021}.

The main results of this work are \cref{thm:1_eq_1}.
\cref{thm:1_eq_1} is stated by McCammond in \cite{mccammond_introduction_2005}. It is not proven there, but it is alluded to being widely accepted as true. Its proof here and the lemmas leading to that proof are the author's own work.
\cref{thm:1_eq_1} is proven by Paolini and Salvetti in \cite{paolini_salvetti_kpi1_2021}. The proof here follows that in \cite{paolini_salvetti_kpi1_2021} but fills in significant details.
The proof of \cref{thm:1_eq_1} largely follows that in \cite{paolini_salvetti_kpi1_2021}. The main original contribution to the proof of \cref{thm:1_eq_1} here is the proof of \cref{thm:proof_overview}, which is omitted in \cite{paolini_salvetti_kpi1_2021}.
Fibre doubling and the concepts explored in \cref{sec:section_example_1} are the authors own work.

For the purpose of creating a functional template, here are some theorems to be referenced in later parts of this document.

\begin{theorem}[{\hspace{1sp}\cite[Theorem 5.5]{paolini_salvetti_kpi1_2021}}]
	\label{thm:1_eq_1}
	\(1=1\)
\end{theorem}
\begin{theorem}[{\hspace{1sp}\cite[Theorem 5.5]{paolini_salvetti_kpi1_2021}}]
	\label{thm:2_eq_2}
	\(2=2\)
\end{theorem}
